---
title: "Sep 6"
output: html_document
---

# Markdown

Document formats:

- Word
- HTML
- PDF
- Markdown

Export to many other formats.

- HTML
- Lightweight
- Markdown variants
  - Original
  - Github
  - Pandoc
- R Markdown calls Pandoc

# Literate Programming

- Write a document
- Have R code inside it
- Runs R code and inserts output for you
- Make changes easily
- Complete record of everything you've done
- Easy verification
- Easy sharing
- Get distributable documents for free

# Relationship between rainfall and harvest

`#` is a section heading.

## Analysis

### Description

I'm working with harvest and rainfall data for the last few years. This is a small dataset. It's all that I have.

```{r}
rain <- c(30, 32, 18, 24, 38, 32)
harvest <- c(150, 145, 55, 70, 180, 150)
plot(rain, harvest, ylim=c(0, 200), xlim=c(0, 50))
abline(a=-75, b=7)
lm(harvest ~ rain)
```

What about R code you don't want to run?

```
lm(harvest ~ rain)
```

The code was: `lm(harvest ~ rain)`

```{r, echo=FALSE}
rain <- c(30, 32, 18, 24, 38, 32)
harvest <- c(150, 145, 55, 70, 180, 150)
plot(rain, harvest, ylim=c(0, 200), xlim=c(0, 50))
abline(a=-75, b=7)
lm(harvest ~ rain)
```

```{r, }
rain <- c(30, 32, 18, 24, 38, 32)
harvest <- c(150, 145, 55, 70, 180, 150)
plot(rain, harvest, ylim=c(0, 200), xlim=c(0, 50))
abline(a=-75, b=7)
lm(harvest ~ rain)
```

- *italics*
- **bold**
- Lists start with `- `
  - Sublist
  - Second sublist item
- Equations $\sum_{i=1}^{4} \xi_{i}$
- Line breaks

This is not
broken.

This is  
broken.

# Estimating the Mean

```{r}
harvest <- c(150, 145, 55, 70, 180, 150)
lm(harvest ~ 1)
mean(harvest)
```

# Steps Ahead

Forecast one step ahead: If data ends in July 2022, predict August 2022.


Forecast two steps ahead: If data ends in July 2022, predict September 2022.

```{r}
data.raw <- read.csv("inflation.csv", header=TRUE)
names(data.raw) <- c("date", "dcpi")
dcpi <- ts(data.raw[,"dcpi"], start=c(1948,1), frequency=12)
library(tstools)
last(dcpi)
```

One step naive forecast: 8.5%

Two step naive forecast: 8.5%

